Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-25 ms.tex

Now, we compare radio emission power of canonical hot Jupiters and that of red giant hot Jupiters.
Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}.
Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows.
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%%
\memoDS{Why scale canonical HJs distances to 5 AU?}
Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission will be even weaker. 
\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
\memoYF{what is the typical wind velocity of AGB stars?}

@@

Combining the expressions above for the dependence of radio emission on planetary magnetic field strength, we find that the radio spectral flux density observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
%&=& P_{\rm radio,\,J} \\
&\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
%%%
&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
%%%
&\approx & 1.12 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
%\\
%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
\end{eqnarray}
%%%
Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}. 
Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.

>>>>

Now, we compare radio emission power of canonical hot Jupiters and that of red giant hot Jupiters.
Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}.
Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows.
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%%
\memoDS{Why scale canonical HJs distances to 5 AU?}
\memoYF{??}
Here, we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission will be even weaker. 
\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
\memoYF{what is the typical wind velocity of AGB stars?}

@@

Combining the expressions above for the dependence of radio emission on planetary magnetic field strength, we find that the radio spectral flux density observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
%&=& P_{\rm radio,\,J} \\
&\approx & 5.22\times 10^{-6} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
%%%
&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_{\star }}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
%%%
&\approx & 1.12 \times 10^{-1} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_{\star }}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.42 \times 10^{-3} \mbox{Jy} \left( \frac{d}{10\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_{\star }}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
%\\
%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
\end{eqnarray}
%%%
Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}. 
Therefore, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them.
